Lyman-$\alpha$ photons through rotating outflows

### 2018-03-28 paper/paper.tex
fig 1 with theta 0 and 90
graficas

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_6}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity}. 
    Here we fix $\tauh=10^6$ and $\theta=90^\circ$.
    We vary \vrot increasing from left to right and \vout increasing from top to
    bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of only outflows,
    but also a Doppler shift from the rotational velocity (thick and dark line).
    \label{fig:doppler_shift}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau7}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau7}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau7}
\end{center}
\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative
  Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
  \label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_logtau6_theta90}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular to the rotation axis}. 
    Here we fix $\tauh=10^6$ and $\theta=90^\circ$.
    We vary \vrot increasing from left to right and \vout increasing from top to
    bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of only outflows,
    but also a Doppler shift from the rotational velocity (thick and dark line).
    \label{fig:doppler_shift}}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_logtau6_theta0}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed parallel to the rotation axis}. 
    Here we fix $\tauh=10^6$ and $\theta=0^\circ$.
    \label{fig:doppler_shift_theta_0}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative
  Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
  \label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}
